---
title: "Report"
author: "ARCA"
date: "4/14/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(emmeans)

# Knitr settings
knitr::opts_chunk$set(echo = FALSE, collapse = TRUE)

# ggplot settings
theme_set(theme_bw())

# Load custom functions
devtools::load_all("../DESCRIPTION")

# Load cached objects
targets::tar_config_set(store = "../analysis/_targets/")
tar_load_report()
```

# Introduction

The aim of the study is to assess the relationship between attachment towards the mother and   social emotional problems in children in the 3rd and 4th year of primary school.

# Descriptive Statistics

Data structure.

```{r, echo=TRUE}
str(my_data)
```

Variables summary.

```{r, echo=TRUE}
summary(my_data)
```

Number of children according to gender and grade.

```{r}
table(my_data$gender, my_data$grade)
```

Externalizing problems distribution.

```{r}
plot_bar(my_data, var = ext_tot)
```

Externalizing problems according to gender and grade.
```{r, echo = TRUE}
get_group_summary(my_data, var = ext_tot, group_by = c("gender", "grade"))
```

```{r}
plot_bar(my_data, var = ext_tot) +
  facet_grid(grade~gender)
```

Relation between externalizing problems and mother attachment according to gender and grade.

```{r}
plot_scatter(my_data, x = ssm_tot, y = ext_tot) +
  facet_grid(grade~gender)
```

# Statistical Analysis

Three-way interaction linear model.

```{r, echo=TRUE}
summary(fit)
```

Model effects.

```{r, echo=TRUE}
car::Anova(fit)
```

Post hoc tests.

```{r, echo=TRUE}
ext_emmeans
```


```{r}
plot_effect_interaction(fit)
```

