---
title: "Report"
author: "ARCA"
date: "4/14/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, collapse = TRUE)
rm(list = ls())
```

# Introduction

The aim of the study is to assess the relationship between attachment towards the mother and   social emotional problems in children in the 3rd and 4th year of primary school.

# Descriptive Statistics

```{r}
my_data <-readxl::read_excel("att-quest.xlsx")
my_data <- as.data.frame(my_data)

# Data munging

my_data$id = factor(my_data$id)
my_data$grade = factor(my_data$grade)
my_data$gender<-factor(my_data$gender)

# Compute questionnaire score

#  - ssm
my_data$ssm1 = abs(my_data$ssm1 - 5)
my_data$ssm3 = abs(my_data$ssm3 - 5)
my_data$ssm4 = abs(my_data$ssm4 - 5)
my_data$ssm9 = abs(my_data$ssm9 - 5)
my_data$ssm10 = abs(my_data$ssm10 - 5)
my_data$ssm13 = abs(my_data$ssm13 - 5)
my_data$ssm15 = abs(my_data$ssm15 - 5)

my_data$ssm_tot <- (my_data$ssm1 +my_data$ssm2+ my_data$ssm3 +my_data$ssm4+my_data$ssm5 +my_data$ssm6+my_data$ssm7 + my_data$ssm8+my_data$ssm9+
  my_data$ssm10+ my_data$ssm11+my_data$ssm12+my_data$ssm13+my_data$ssm14 + my_data$ssm15)/15

# - sdq

my_data$sdq7 = abs(my_data$sdq7 - 2)
my_data$sdq11 = abs(my_data$sdq11 - 2)
my_data$sdq14 = abs(my_data$sdq14 - 2)
my_data$sdq21 = abs(my_data$sdq21 - 2)
my_data$sdq25 = abs(my_data$sdq25 - 2)

my_data$int_tot<-my_data$sdq3+my_data$sdq6+my_data$sdq8 +my_data$sdq11+ my_data$sdq13+my_data$sdq14 + 
  my_data$sdq16+my_data$sdq19+my_data$sdq23+my_data$sdq24
my_data$ext_tot<-my_data$sdq2+my_data$sdq5+ my_data$sdq7+my_data$sdq10 +my_data$sdq12+my_data$sdq15 +
  my_data$sdq18+my_data$sdq21+ my_data$sdq22 +my_data$sdq25

my_data =my_data[, c("id", "grade", "gender", "ssm_tot", "int_tot", "ext_tot")]

```

Data structure.

```{r, echo=TRUE}
str(my_data)
```

Variables summary.

```{r, echo=TRUE}
summary(my_data)
```

Number of children according to gender and grade.

```{r}
table(my_data$gender, my_data$grade)
```

Externalizing problems distribution.

```{r}
library('ggplot2')
theme_set(theme_bw())

ggplot(my_data) +
  geom_bar(aes(x = ext_tot), fill = "firebrick", alpha = .8)
```

Externalizing problems according to gender and grade.
```{r, echo = TRUE}
# Mean
tapply(my_data$ext_tot, INDEX = list(my_data$gender, my_data$grade), FUN = mean)

# SD
tapply(my_data$ext_tot, INDEX = list(my_data$gender, my_data$grade), FUN = sd)
```

```{r}
ggplot(my_data) +
  geom_bar(aes(x = ext_tot), fill = "firebrick", alpha = .8)+
  facet_grid(grade~gender)
```

Relation between externalizing problems and mother attachment according to gender and grade.

```{r}
ggplot(my_data) +
  geom_jitter(aes(x = ssm_tot, y = ext_tot), width= .01, height = .2) +
  facet_grid(grade~gender)
```

# Statistical Analysis

Three-way interaction linear model.

```{r, echo=TRUE}
fit <-lm(ext_tot ~ ssm_tot * gender * grade, data = my_data)
summary(fit)
```

Model effects.

```{r, echo=TRUE}
car::Anova(fit)
```

Post hoc tests.

```{r, echo=TRUE}
ext_emmeans <- emmeans::emtrends(fit, pairwise ~ grade*gender, var = 'ssm_tot', adjust = "mvt")
ext_emmeans
```


```{r}
ggplot(as.data.frame(effects::effect("ssm_tot * gender * grade", fit, xlev = 20))) +
  geom_ribbon(aes(x= ssm_tot, ymin = lower, ymax=upper, fill =gender), alpha = .4) +
  geom_line(aes(x= ssm_tot, y = fit, color =gender), size = 1.2) +
  geom_rug(data = my_data[my_data$gender == 0,],
           aes(x= ssm_tot, color = gender, y = ext_tot), size = 1.2, alpha = .7,
           position = position_jitter(width = .02, height = 0), sides = "t") +
  geom_rug(data = my_data[my_data$gender == 1,],
           aes(x= ssm_tot, color = gender, y = ext_tot), size = 1.2, alpha = .7,
           position = position_jitter(width = .02, height = 0), sides = "b") +
  facet_grid(grade~.) +
  theme(legend.position = "top")
```

